Solar wind discontinuities spatial evolution in the outer heliosphere

### 2024-02-14 article.qmd
update

::: {#fig-overview layout-ncol=1}
![](figures/juno_orbit_white){}

![](figures/juno-hg-loc_sunspot-number){#fig-hg-loc-sunspot}

Juno orbit, its longitudinal difference with Earth & STEREO missions and sunspot number during its cruise phase

@@

![Near-Earth's and STEREO-A solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-overview}

>>>>

:::: column-screen-inset
::: {#fig-overview}

<!-- ![](figures/juno_orbit_white){#fig-orbit width=85%} -->

<!-- ![](figures/juno-hg-loc_sunspot-number){#fig-hg-loc-sunspot} -->

![](figures/fig_overview)

Juno orbit, its longitudinal difference with Earth & STEREO missions, sunspot number during its cruise phase and near-Earth’s and STEREO-A solar wind plasma data during JUNO cruise phase

:::
::::

@@

<!-- ![Near-Earth's and STEREO-A solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-overview} -->
